Efficiency and acoustic considerations for pumpjets in the context of conventionally powered submarines

### 2017-12-30 DraftExec.Rnw
little pic reference

\title{Efficiency}
\author{Aidan Morrison}

@@

It is only when the water is all at a much higher temperature that the bubbles remain their full size for long enough to detatch and rise all the way to the surface, a process we typically think of as boiling water.  It is worthwhile noting that the sound emitted at this stage is much softer and lower than the early onset of cavitation. Larger bubbles result in lower frequencies of sound being emitted. Even at higher temperature, the rougher parts of the surface provide the points where all the cavitation originate.

>>>>

\title{Efficiency and acoustic considerations for pumpjets in the context of conventionally powered submarines}
\author{Aidan Morrison}

@@

It is only when the water is all at a much higher temperature that the bubbles remain their full size for long enough to detatch and rise all the way to the surface, a process we typically think of as boiling water, as shown in Figure ~\ref{fig:BoilingCavitation.JPG}.  It is worthwhile noting that the sound emitted at this stage is much softer and lower than the early onset of cavitation. Larger bubbles result in lower frequencies of sound being emitted. Even at higher temperature, the rougher parts of the surface provide the points where all the cavitation originate.

### 2017-12-30 DraftExec.tex
little pic reference

\title{Efficiency}
\author{Aidan Morrison}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

In contrast, the Collins Class Submarine's main motor is rated at less than 6MW, with designs for the future submarine appearing to be only slightly larger \parencite{patrick2012}.  It is fair to say that in terms of maximum power ouput, nuclear submarines could have something like 5-10 times as much power at their disposal, and their **peak** output.

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{XenonPoison.png}
\caption{Xenon poisoning effect following shutdown \parencite{garland2005}}
\label{fig:XenonPoison.png}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{BoundaryLayer.png}
\caption{The development of a boundary layer \parencite{mollard2011}}
\label{fig:BoundaryLayer.png}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{LaminarTurbulent.png}
\caption{A simple comparison of laminar and turbulent flows from \citetitle{NPdotnet2017} \citeyear{NPdotnet2017}}
\label{fig:LaminarTurbulent.png}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{EarlyCavitation.JPG}
\caption{Cavitation bubbles form and collapse creating noise and some tiny bubbles long before boiling occurs}
\label{fig:EarlyCavitation.JPG}
\end{figure}

It is only when the water is all at a much higher temperature that the bubbles remain their full size for long enough to detatch and rise all the way to the surface, a process we typically think of as boiling water.  It is worthwhile noting that the sound emitted at this stage is much softer and lower than the early onset of cavitation. Larger bubbles result in lower frequencies of sound being emitted. Even at higher temperature, the rougher parts of the surface provide the points where all the cavitation originate.

\begin{figure}
\includegraphics[width=0.9\textwidth]{BoilingCavitation.JPG}
\caption{Only at very high temperatures do the bubbles endure at full-size in the water and reach the surface}
\label{fig:BoilingCavitation.JPG}
\end{figure}

@@

>>>>

\title{Efficiency and acoustic considerations for pumpjets in the context of conventionally powered submarines}
\author{Aidan Morrison}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

In contrast, the Collins Class Submarine's main motor is rated at less than 6MW, with designs for the future submarine appearing to be only slightly larger \parencite{patrick2012}.  It is fair to say that in terms of maximum power ouput, nuclear submarines could have something like 5-10 times as much power at their disposal, and their \textbf{peak} output.

@@

\begin{figure}
\includegraphics[width=\textwidth]{XenonPoison.png}
\caption{Xenon poisoning effect following shutdown \parencite{garland2005}}
\label{fig:XenonPoison.png}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{BoundaryLayer.png}
\caption{The development of a boundary layer \parencite{mollard2011}}
\label{fig:BoundaryLayer.png}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{LaminarTurbulent.png}
\caption{A simple comparison of laminar and turbulent flows from \citetitle{NPdotnet2017} \citeyear{NPdotnet2017}}
\label{fig:LaminarTurbulent.png}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{EarlyCavitation.JPG}
\caption{Cavitation bubbles form and collapse creating noise and some tiny bubbles long before boiling occurs}
\label{fig:EarlyCavitation.JPG}
\end{figure}

It is only when the water is all at a much higher temperature that the bubbles remain their full size for long enough to detatch and rise all the way to the surface, a process we typically think of as boiling water, as shown in Figure ~\ref{fig:BoilingCavitation.JPG}.  It is worthwhile noting that the sound emitted at this stage is much softer and lower than the early onset of cavitation. Larger bubbles result in lower frequencies of sound being emitted. Even at higher temperature, the rougher parts of the surface provide the points where all the cavitation originate.

\begin{figure}
\includegraphics[width=\textwidth]{BoilingCavitation.JPG}
\caption{Only at very high temperatures do the bubbles endure at full-size in the water and reach the surface}
\label{fig:BoilingCavitation.JPG}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{FlowSeparation.png}
\caption{Flow separation involves flow reversal near a surface when a fluid is moving against an adverse pressure gradient, as shown in \parencite{mollard2011}}
\label{fig:FlowSeparation.png}
\end{figure}
